Model

### 2019-04-16 stats/model.Rmd
first pass model inferring semantic strength

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)

@@

# Ignore: Model for ME Effect
```{r}
me_data <- read_csv("../data/child_basic_me.csv")%>%
    filter(trial != "train1",
           trial != "train2")%>%
  mutate(z_age = age_num - mean(age_num))

@@

saveRDS(me_model, "../saves/me_effect_model.rds")

@@

age_me_effect <- as_tibble(ranef$familiar, rownames = "familiar")%>%
  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_slope = fixef%>%filter(term=="z_age")%>%pull(Estimate))%>%
  group_by(familiar) %>%
  expand(Estimate.Intercept,Estimate.z_age,grand_intercept,grand_slope,z_age = me_data$age_num - mean(me_data$age_num), mean_age = mean(me_data$age_num))%>%
  mutate(me_effect = plogis(grand_intercept + Estimate.Intercept+(Estimate.z_age+grand_slope)*z_age), 
         age = z_age+mean_age)%>%
  select(familiar, me_effect, age)

@@

>>>>

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)

@@

## For comparison: GLMM for ME effect and data
```{r}
me_data <- read_csv("../data/child_basic_me.csv")%>%
    filter(trial != "train1",
           trial != "train2")%>%
  mutate(z_age = age_num - mean(age_num))

@@

#saveRDS(me_model, "../saves/me_effect_model.rds")

@@

age_me_effect <- as_tibble(ranef$familiar, rownames = "familiar")%>%
  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_slope = fixef%>%filter(term=="z_age")%>%pull(Estimate))%>%
  group_by(familiar) %>%
  expand(Estimate.Intercept,Estimate.z_age,grand_intercept,grand_slope,z_age = me_data$age_num - mean(me_data$age_num), mean_age = mean(me_data$age_num))%>%
  mutate(me_effect = plogis(grand_intercept + Estimate.Intercept+(Estimate.z_age+grand_slope)*z_age), 
         age = z_age+mean_age)%>%
  select(familiar, me_effect, age)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))

model_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = familiar))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Model")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")

p2 <- read_csv("../data/child_basic_me.csv")%>%
  filter(trial != "train1",
         trial != "train2")%>%
    left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))

data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(~familiar)+
  ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")

@@

```{r}
ggarrange(data_plot,model_plot, common.legend = T, legend = "right")
```
